A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2015-10-22 imaging_demo/ms.tex

\subsection{Calibration}

>>>>

\subsection{Calibration}
Calibration of direct imaging correlator remains an unresolved matter. Contrary
to the FX data flow, direct imagers mix the signals from all antennas before
averaging and writing to disk. It is therefore essential to apply gain solutions 
before the gridding step. Previous efforts have resorted to applying FX-generated
calibration solutions \citep{zhe14, fos14}, or integrate a dedicated FX correlator 
which periodically forms the full visibility matrix \citep{wij09, dev09}.

In a companion paper to appear soon, we demonstrate a novel calibration 
technique (EPICal) which leverages the data products formed by direct imaging 
correlators to estimate antenna complex gains. This method correlates the antenna 
electric field signals with an image pixel form the output of the correlator in the 
feedback calibration fashion outlined in \citealt{mor11} (illustrated in Figure 
\ref{fig:MOFF-flowchart} by the arrow leading from the imager to the calibration 
block). Furthermore it allows for arbitrarily complex sky models, and following the 
MOFF algorithm places no restriction on array layout, and accounts for non-identical 
antenna beam patterns. Because only a single correlation is needed for each 
antenna, the computation complexity scales only as $N_{\mathrm{ant}}$.

The calibration module included in the EPIC repository allows for application of pre-
determined calibration solutions, or can solve for the complex gains using the 
EPICal algorithm.
